A community-maintained standard library of population genetic models

### 2020-04-16 popSimManu.tex

The \stdpopsim library has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its quality.
Importantly, we have rigorous quality control methods to ensure that models
are correctly implemented with respect to their original publication 
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community (https://stdpopsim.readthedocs.io/en/latest/development.html).
Below we describe the resource and give
examples of how it can be used to benchmark demographic inference methods.

>>>>

The \stdpopsim library has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its quality.
Importantly, we have rigorous quality control methods to ensure that we have
correctly implemented the models as described in their original publication
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community (https://stdpopsim.readthedocs.io/en/latest/development.html).
Below we describe the resource and give
examples of how it can be used to benchmark demographic inference methods.
